RIScatter: Unifying Backscatter Communications and Reconfigurable Intelligent Surface From a Probabilistic Perspective

### 2022-11-11 assets/illustration/energy_distribution.tex
:paintbrush: Update illustration function

		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,1)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_1)$}

		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.6)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_2)$}

		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.4)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_3)$}

		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.28)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
		\draw[latex-latex] (0,0) -- (12.78,0) node[above,midway,yshift=-2]{$\mathcal{R}_1$};
		\draw[latex-latex] (12.78,0) -- (20.28,0) node[above,midway,yshift=-2]{$\mathcal{R}_2$};
		\draw[latex-latex] (20.28,0) -- (29.62,0) node[above,midway,yshift=-2]{$\mathcal{R}_3$};
		\draw[latex-latex] (29.62,0) -- (70,0) node[above,midway,yshift=-2]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

>>>>

		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,1)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_1)$}

		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.6)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_2)$}

		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.4)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_3)$}

		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.28)};
		\addlegendentryexpanded{$f(z \mid \mathcal{H}_4)$}
		\draw[latex-latex] (0,0) -- (12.78,0) node[above,midway,yshift=-2]{$\mathcal{R}_1$};
		\draw[latex-latex] (12.78,0) -- (20.28,0) node[above,midway,yshift=-2]{$\mathcal{R}_2$};
		\draw[latex-latex] (20.28,0) -- (29.62,0) node[above,midway,yshift=-2]{$\mathcal{R}_3$};
		\draw[latex-latex] (29.62,0) -- (70,0) node[above,midway,yshift=-2]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}
